|

### 2023-05-10 paper/02-data.Rmd
more captions

Table \ref{tab:track} displays a tracking data example for a play from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ended with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack].
In addition, Figure \ref{fig:fig_field_raw} presents the locations of every Las Vegas (in black) and Denver (in orange) player on the field from this play at 1, 2, 3 and 4 seconds after the ball snap, with Maxx Crosby highlighted in blue.

>>>>

Table \ref{tab:track} displays a tracking data example for a play from the 2021 NFL regular season week six matchup between the Las Vegas Raiders and Denver Broncos, which ends with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack].
In addition, Figure \ref{fig:fig_field_raw} presents the locations of every Las Vegas (in black) and Denver (in orange) player on the field from this play at 1, 2, 3 and 4 seconds after the ball snap, with Maxx Crosby highlighted in blue.

### 2023-05-10 paper/04-results.Rmd
more captions

```{r}
#| label: fig_crosby_curves
#| fig.cap: "The change in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a unsuccessful pass rush play that results in a sack."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this play, Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass[^unsuccess].
We see that the STRAIN generated by Crosby and other pass rushers are relative small for this play, compared to the previous play which resulted in a sack.

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "The change in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of an unsuccessful pass rush play."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions"
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves
```

```{r}
#| label: fig_outcome_curves
#| fig.cap: "STRAIN curves for different positions by outcome"
#| fig.width: 6.5
#| fig.height: 2.7
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves
```

@@

```{r}
#| label: fig_stability
#| fig.cap: "Relationships between average STRAIN for the last and first 4 weeks of the 2021 NFL season. A strong linear correlation ($r = 0.854$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals generated by sampling from the posterior distributions via parametric bootstrapping using the `merTools` package [@knowlesmerTools, @gelman2006data]. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rushers. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero.
[NEED TO THINK ABOUT WHAT MORE TO SAY HERE]

>>>>

```{r}
#| label: fig_crosby_curves
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a successful pass rush play that results in a sack."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this play, Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass[^unsuccess].
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play shown in Figure \ref{fig:fig_crosby_curves} which results in a sack.

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of an unsuccessful pass rush play."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions. Edge rushers (OLB and DE) tend to generate more STRAIN than interior rushers (DT and NT). The dotted gray line represents the average STRAIN curve for all players without accounting for position."
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves
```

```{r}
#| label: fig_outcome_curves
#| fig.cap: "Positional STRAIN curves by play outcome (sack, hit, hurry, and none)."
#| fig.width: 6.5
#| fig.height: 2.7
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves
```

@@

```{r}
#| label: fig_stability
#| fig.cap: "Relationship between average STRAIN for the last and first 4 weeks of the 2021 NFL season. A strong linear correlation ($r = 0.854$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals generated by sampling from the posterior distributions via parametric bootstrapping using the `merTools` package [@knowlesmerTools, @gelman2006data]. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero.
[NEED TO THINK ABOUT WHAT MORE TO SAY HERE]
